GlobalSearchRegression.jl \\ \vspace{5mm} REPORT

### 2019-07-23 src/Output/decorations/latex/tpl.tex
Export zip from temporal folder

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}    \\
                    & {{kfolds}}-fold         & {{kfolds}}-fold \\
    Variables       & Mean                    & Median          \\
    \hline
    \hline
{{ median }}

--

{{ average }}

    {{#kfoldvars}}
      {{ varname }} & {{ meancoef }}{{stars}} & {{ mediancoef }}{{stars}} \\
                    & {{ meanstd }}           & {{ medianstd }}           \\
    {{/kfoldvars}}
    \hline

>>>>

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}    \\
                    & {{kfolds}}-fold         & {{kfolds}}-fold \\
    Variables       & Mean                    & Median          \\
    \hline
    \hline
{{ median }}
--
{{ average }}
    {{#kfoldvars}}
      {{ varname }} & {{ meancoef }}{{stars}} & {{ mediancoef }}{{stars}} \\
                    & {{ meanstd }}           & {{ medianstd }}           \\
    {{/kfoldvars}}
    \hline
